\documentclass{resume} % Use the custom resume.cls style
\usepackage{fontawesome}
\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Ayesha Nagdawala} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{\href{mailto:ayesha.m.nagdawala@gmail.com}{ayesha.m.nagdawala@gmail.com} \\ \faGithub {}
\href{https://github.com/AyeshaNagdawala}{github.com/AyeshaNagdawala} \\ \faLinkedinSquare {} \href{https://www.linkedin.com/in/ayeshanagdawala/}{linkedin.com/in/AyeshaNagdawala}
}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\begin{rSection}{EDUCATION}



\textbf{University of Mumbai – Thadomal Shahani Engineering College (TSEC) }\hfill {Expected 2025}

\textit{{Bachelor of Engineering in Information Technology (CGPA: 9.47 / 10.0) }}


\begin{itemize}
\item \textbf{Coursework}: Data Structure and Analysis, Database Management System, Paradigms and Computer, Programming Fundamentals, Computer Network and Network Design, Operating System,  Computer Organization and Architecture, Automata Theory, Principle of Communication, Engineering Mathematics
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Frontend : & HTML, CSS, Bootstrap\\
Backend : & Flask\\
Database : & SQLite, MySQL\\
\end{tabular}
\hfill% move it to the right
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages : & C, C++, Java, Python\\
Platforms : & Github, PythonAnywhere\\
Tools : & Shell, Vim, Git\\

\end{tabular}


\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{CodeStorm} \hfill August 2022 - Current\\
Core Committee Member \hfill \textit{TSEC, Mumbai, India}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Organized technology focusing events for college students.
     \item Marketing and Public Relations communicating with sponsors.\item Handling offline flagship CODEISSANCE Hackathon with over 200 participants.
 \end{itemize}

 
\textbf{Bukr} \textit{ED - TECH STARTUP}\hfill Oct 2021 - Dec 2021\\
Technical Brand Marketing Intern \hfill \textit{Mumbai, India}
\\ \\ The internship required responsibilities like managing data, providing technical training for interns, executing targeted online advertisements, overseeing social media management, facilitating online workshops, managing associates, nurturing sales leads, engaging with customers, and potentially other related responsibilities.





\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Better Mind} {\hfill \textit{HTML, CSS, JS, SQLite, Flask }}
{\\\textit{A 360 degree mental health monitoring web app.}\\ Better Mind offers a wide range of features to help individuals monitor their well-being and get support when needed example - mood tracking, daily journaling, anxiety tests, help resources and an live search monitoring with active mental health coefficient grading. \href{https://github.com/AyeshaNagdawala/bettermind}{(View Repo)}}
\item \textbf{Pass Vault} {\hfill \textit{Java, Swing, MySQL }}
{\\\textit{An intuitive and secure password manager.} \\ Password Manager built for the next million people connecting to the internet for the first time, uses hashing and AES-256 Encryption. Supports random password generation, periodic reminders and more. \href{https://github.com/AyeshaNagdawala/passvault/} {(View Repo)}}
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular and Leadership} 
\begin{itemize}
    \item 	\href{https://www.linkedin.com/posts/dr-gopal-pardesi-9059968_tsec-it-dept-rocks-project-competition-activity-6997511090406371328-h9w5?utm_source=share&utm_medium=member_desktop/} {\textbf{First Runner up}} in Javagenix Hackathon. Organized by TSEC,Bandra. Conducted on 27th Oct 2022.
\end{itemize}
\begin{itemize}
    \item \href{https://www.linkedin.com/feed/update/urn:li:activity:7026184654688792576/} {\textbf{Second Position}} in Bit N Build : Open Innovation Hackathon. Organized by Google Developers Student Club (FRCE x UMIT). Conducted on 29th Jan 2023.
\end{itemize}
\begin{itemize}
    \item  \href{https://stagneshighschool.org/farewell-std-x/}{\textbf{Star Agnesian for others}} awarded at Agnesian Award Ceremony, an achievement which is awarded to a pupil who possesses every standard that the school envisions. (5 in 250+)
\item Titled as \textbf{The most deserving student} in the middle school as well as highschool for being an all rounder student and balancing the academics with extra curricular activities. (1 in 250+)
\end{itemize}
\end{rSection}

\end{document}
